---
title             : "COVID-19 Child & Adolescent Mental Health and Parenting Study"
shorttitle        : "COVID-ChAMPS"

author: 
  - name          : "Sarah Whittle"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "swhittle@unimelb.edu.au"
  - name          : "Other authors"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Melbourne Neuropsychiatry Centre (MNC), Department of Psychiatry, The University of Melbourne & Melbourne Health, Melbourne, Australia"
  - id            : "2"
    institution   : "Other Institute"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.


  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
\ output            : papaja::apa6_pdf
output            : papaja::apa6_word


---

```{r setup, include = FALSE}

#papaja needs to be downloaded from github - instructions here - https://github.com/crsh/papaja

library(papaja)
library(psych)
library(dplyr)
library(corrplot)
library(corx)
r_refs("r-references.bib")

#read in data
covid_data <- read.csv("scored_data/covid_data_scored.csv", header=TRUE, stringsAsFactors = FALSE)
covid_data_child <- read.csv("scored_data/covid_data_child_scored.csv", header=TRUE, stringsAsFactors = FALSE)
SDQ.c.freq <- read.csv("scored_data/SDQ.c.freq.csv", header=TRUE, stringsAsFactors = FALSE)

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

## Reproducible table section


## Things to do:
N's/stats for the sample used in analysis (i.e., those that completed SDQ1 or PTSD, n parents is 381):
Frequencies,% for demographic info - gender of parent and children, country, income, edu, occupation, ethnicity, biological vs other relationship to child
 stay at home (Y/N), stay at home length,  job change
SDQ change since COVID - M/SD + frequencies based on number of items where more is reported (something to indicate the extent of kids who had worsening problems)

```{r, desctable, echo=FALSE, results='asis'}

#create matrix with the values in there
## to do - combine other and non-binary
par_gender <- summarytools::freq(covid_data$par_gender, order = "freq")[c(1:5), c(1,4)]
par_age <- cbind(mean(covid_data$par_age, na.rm =TRUE), sd(covid_data$par_age, na.rm =TRUE))
ch_gender <- summarytools::freq(covid_data_child$ch_gender, order = "freq")[c(1:5), c(1,4)]
ch_age <- cbind(mean(covid_data_child$ch_age, na.rm =TRUE), sd(covid_data_child$ch_age, na.rm =TRUE))
country <- summarytools::freq(as.factor(covid_data$country_cat), order = "levels")[c(1:5), c(1,2)]
par_ed_fac <-summarytools::freq(as.factor(covid_data$par_ed_ord)) [c(1:11), c(1,4)]
other_par<- summarytools::freq(as.factor(covid_data_child$other_par))[c(1:3), c(1,4)]

#rearrange the levels first so they are in order lowest wage to highest
covid_data$income <- factor(covid_data$income, levels = c("> AU$36,400 (US$23,230) per year", "Up to AU$699 per week (AU$36,400 or US$23,230 per year)", "AU$700 to AU$999 per week (up to AU$52,000 or US$33,168 per year)", "AU$1,000 to AU$1,730 per week (up to AU$90,000 or US$57,407 per year)", "AU$1,731 to AU$2,700 per week (up to AU$140,000 or US$89,307 per year)", "Above AU$140,000 (US$89,307) per year", "Prefer not to say"))

income <- summarytools::freq(as.factor(covid_data$income))[c(1:8), c(1,4)]

#work in progress number of children answered for
# child_answered_na<- summarytools::freq(as.factor(covid_data_child$id))["<NA>",1]
# child_answered<- summarytools::freq(as.factor(covid_data_child$id))[,1]
# summarytools::freq(as.factor(child_answered))

desctable<- rbind( country, par_gender, ch_gender, par_age, ch_age, par_ed_fac, other_par, income)



row.names(desctable) <- c("Australia", "U.K.", "U.S.A","New Zealand","Other", "Female","Male","Non-binary/gender-fluid","Other","Missing", "Female","Male","Non-binary/gender-fluid","Other","Missing",
                          "Parent Age", "Child Age",
                          "Partial primary school", "Completed primary school", "Partial high school",  "Completed high school","TAFE","Partial University","Graduated Bachelor's degree","Honors degree","Partial graduate school","Completed graduate school", "Missing", "No", "Yes", "Missing", "Less than AU$36,400 per year", "Up to AU$36,400 per year", "Up to AU$52,000 per year", "Up to AU$90,000 per year", "Up to AU$140,000 per year)", "> AU$140,000 per year", "Prefer not to say", "Missing")

apa_table(
  list(`Country` = desctable[1:5,], `Age` = desctable[c(16,17),],`Parent Gender` = desctable[c(6:10),], `Child Gender` = desctable[c(11:15),], `Parent Education` = desctable[c(18:28),] , `Another parent in the home` = desctable[c(29:31),], `Household income` = desctable[c(32:39),]),
          caption = "Descriptive statistics",
          #note = "",
          align = c("l",rep("c", 2)),
          col.names = c( "Demographic measure","Frequency (or Mean)","Percentage (or Stnd. Dev.)"),
  digits = c(0,0,2),
  font_size = "small"
  )

```

```{r, clindesctable, echo=FALSE, results='asis'}
#table to diplay clinical cutt-offs
#DASS
## Order the levels for the freq
DASSlevels <- c("Normal", "Mild", "Moderate", "Severe", "Ex_severe")

covid_data$DepCat <- factor(covid_data$DepCat, levels = DASSlevels)
D<- summarytools::freq(as.factor(covid_data$DepCat))[c(1:5), c(1,2)]
covid_data$AnxCat <- factor(covid_data$AnxCat, levels = DASSlevels)
A<- summarytools::freq(as.factor(covid_data$AnxCat))[c(1:5), c(1,2)]
covid_data$StressCat <- factor(covid_data$StressCat, levels = DASSlevels)
S <- summarytools::freq(as.factor(covid_data$StressCat))[c(1:5), c(1,2)]


#SDQ
## Order the levels for the freq
SDQlevels <- c("Average", "S_raised", "High")

covid_data_child$SDQemo_cat <- factor(covid_data_child$SDQemo_cat, levels = SDQlevels)
emo <- summarytools::freq(as.factor(covid_data_child$SDQemo_cat))[c(1:4), c(1,4)]
covid_data_child$SDQcon_cat <- factor(covid_data_child$SDQcon_cat, levels = SDQlevels)
con <- summarytools::freq(as.factor(covid_data_child$SDQcon_cat))[c(1:4), c(1,4)]
covid_data_child$SDQhyp_cat <- factor(covid_data_child$SDQhyp_cat, levels = SDQlevels)
hyp <- summarytools::freq(as.factor(covid_data_child$SDQhyp_cat))[c(1:4), c(1,4)]
covid_data_child$SDQpeer_cat <- factor(covid_data_child$SDQpeer_cat, levels = SDQlevels)
peer <- summarytools::freq(as.factor(covid_data_child$SDQpeer_cat))[c(1:4), c(1,4)]

clin_freq<- rbind(D,A,S, emo, con, hyp, peer)

rownames(clin_freq) <- c("Normal", "Mild", "Moderate", "Severe", "Ext. Severe",
                         "Normal", "Mild", "Moderate", "Severe", "Ext. Severe",
                         "Normal", "Mild", "Moderate", "Severe", "Ext. Severe",
                         "Average", "Slightly Raised", "High","Missing",
                         "Average", "Slightly Raised", "High","Missing",
                         "Average", "Slightly Raised", "High","Missing",
                         "Average", "Slightly Raised", "High","Missing"
                         )

apa_table(
  list(`Depression` = clin_freq[1:5,], `Anxiety` = clin_freq[c(6:10),],`Stress` = clin_freq[c(11:15),], `Emotional Problems` = clin_freq[c(16:19),], `Conduct Problems` = clin_freq[c(20:23),] , `Hyperactivity` = clin_freq[c(24:27),], `Peer Problems` = clin_freq[c(28:31),]),
          caption = "Clinical scales - levels of symptoms",
          #note = "",
          align = c("l",rep("c", 2)),
          col.names = c( "Clinical subscale","Frequency","Percentage"),
  digits = c(0,0,2),
  font_size = "small"
  )

```

```{r, changetable, echo=FALSE, results='asis'}

rownames(SDQ.c.freq) <- c("Fights","Lies","Obedient","Steals","Temper", "Fears", "Headaches" ,
                         "Nervous", "Unhappy" , "Worries", "Attention" ,"Distracted","Fidget",
                         "Restless" ,"Thinks","Adults", "Bullied" , "Friend" , "Liked" , 
                         "Solitary" )

apa_table(
  SDQ.c.freq[, c(6:8)],
          caption = "Percentage change in children's symptoms",
          #note = "",
          align = c("l",rep("c", 3)),
          col.names = c("Symptom", "More","Same","Less"),
  digits = c(0,2,2,2),
  font_size = "small",
  stub_indents = list("Conduct" = c(1:5), "Emotional" = c(6:10), "Hyperactivity" = c(11:15), "Peer" = c(16:20))
  )

```


```{r, covdesctable, echo=FALSE, results='asis'}
# participants were locked down at the time, kids in school or working from home at the time of survey

#empty dataframe
lckdwn=data.frame(matrix(ncol=2,nrow=3))

#Still in lockdown
lckdwn[1,1] <-  summarytools::freq(as.factor(covid_data$stay_home))["Yes",1]-summarytools::freq(as.factor(covid_data$leave_home))["Yes",1]
#Were in lockdown - now lifted
lckdwn[2,1] <- summarytools::freq(as.factor(covid_data$stay_home))["Yes",1]-summarytools::freq(as.factor(covid_data$leave_home))["No",1]
#no stay at home yet
lckdwn[3,1] <- summarytools::freq(as.factor(covid_data$stay_home))["No",1]
#make the percentages
lckdwn[1,2]<- (lckdwn[1,1]/(lckdwn[1,1]+lckdwn[2,1]+lckdwn[3,1]))*100
lckdwn[2,2]<- (lckdwn[2,1]/(lckdwn[1,1]+lckdwn[2,1]+lckdwn[3,1]))*100
lckdwn[3,2]<- (lckdwn[3,1]/(lckdwn[1,1]+lckdwn[2,1]+lckdwn[3,1]))*100

rownames(lckdwn) <- c("Current", "Past", "No")

# Do the same for schools
chhome=data.frame(matrix(ncol=2,nrow=4))

#Child at home due to COVID current
chhome[1,1] <-  (summarytools::freq(as.factor(covid_data$ch1_school))["Yes",1] +
  summarytools::freq(as.factor(covid_data$ch1_school))["No, but I kept my child home from school (chose to or was encouraged to)",1])-
  summarytools::freq(as.factor(covid_data$ch1_reopen))["Yes",1]
#Was at home past
chhome[2,1] <- summarytools::freq(as.factor(covid_data$ch1_reopen))["Yes",1]
#Child home schholed
chhome[3,1] <- summarytools::freq(as.factor(covid_data$ch1_school))["My child is home schooled",1]
#not home
chhome[4,1] <- summarytools::freq(as.factor(covid_data$ch1_school))["No",1]
#make the percentages
chhome[1,2]<- (chhome[1,1]/summarytools::freq(as.factor(covid_data$ch1_school))["Total",1])*100
chhome[2,2]<- (chhome[2,1]/summarytools::freq(as.factor(covid_data$ch1_school))["Total",1])*100
chhome[3,2]<- (chhome[3,1]/summarytools::freq(as.factor(covid_data$ch1_school))["Total",1])*100
chhome[4,2]<- (chhome[4,1]/summarytools::freq(as.factor(covid_data$ch1_school))["Total",1])*100

rownames(chhome) <- c("Current", "Past","Home School", "No")
```

```{r, corrtable, echo=FALSE, results='asis'}

#correlation table
#first matrix - par vars only
corrmatrixpar <-  dplyr::select(covid_data, par_age, par_gender_num, par_ed_ord, income_famsize, DASSDep, DASSAnx, DASSStress, covid_neg_num, covid_pos_num)
#include both par and child vars
corrmatrixch <-  dplyr::select(covid_data_child, par_age, par_gender_num, par_ed_ord, income_famsize, DASSDep, DASSAnx, DASSStress,covid_neg_num, covid_pos_num,
                               ch_age, ch_gender_num, SDQemo, SDQcon, SDQhyp, SDQpeer, SDQpro, SDQemo2, SDQcon2, SDQhyp2, SDQpeer2, SDQpro2,PARQwarmth, PARQhostile, PARQwarmth, PARQhostile, PARQneglect, PARQundiff, PARQcontrol,facts_comm, emotion_comm, self_comm)

#insert colnames here
#colnames(corrmatrixpar) <- c()


xp <- corx(corrmatrixpar,
          triangle = "lower",
          stars = c(0.05, 0.01, 0.001))

xc <- corx(corrmatrixch,
          triangle = "lower",
          stars = c(0.05, 0.01, 0.001))

#replace the par-par correlations from the child table with the ones from the par table so that they have the correct N.
xc$apa[1:9,1:8] <- xp$apa

papaja::apa_table(xc$apa, # apa contains the data.frame needed for apa_table
                  caption = "Bivariate correlations for key variables and covariates (Pearson’s)",
                  note = "* p < 0.05; ** p < 0.01; *** p < 0.001. Not corrected for multiple comparisons. Full variable names: .",
                  landscape = TRUE,
                  longtable = TRUE,
                  small = TRUE
                  #escape = F
                  )

#%>%
 # kable_styling(full_width = T)

#correlation plot
# M <- cor(corrmatrix, use = "complete.obs")
# colnames(M) <- c("facts", "information", "child emotions", "parent emotions", "others' feelings", "reassurance", "didn't know what to say", "too upset")
# rownames(M) <- c("facts", "information", "child emotions", "parent emotions", "others' feelings", "reassurance", "didn't know what to say", "too upset")
# res1 <- cor.mtest(corrmatrix, use = "complete.obs",
#                    conf.level = .95)
#  
# corrplot.mixed(M,  order = "hclust", lower.col = "black", number.cex = .6,
#                 tl.col = "black", tl.srt = 45,tl.cex = 0.8, tl.pos= "lt",
#                 p.mat = res1$p, sig.level = .05, insig = "blank") 

```

```{r, main_varstable, echo=FALSE, results='asis'}


#Mean, SD, range for continuous vbls - DASS Dep & Anx & Stress, FES, PARQ hostile & warmth, 
# SDQ emo, hyp, con, peer, PTSD 
# + Ns/% in each group based on clinical cut-off's (DASS, PARQ, SDQ).
# add in communication vars

#Select the variables to go in

analysis_vars_par<- dplyr::select(covid_data, DASSDep, DASSAnx, DASSStress, totalFES)
analysis_vars_child<- dplyr::select(covid_data_child, PARQhostile, PARQwarmth, 
              SDQemo, SDQhyp, SDQcon, SDQpeer, totalPTSD, facts_comm, emotion_comm, self_comm, covid_neg_num, covid_pos_num )

#provides mean, sd, kurtosis, skew etc
desc.p <- describe(analysis_vars_par)
desc.c <- describe(analysis_vars_child)
desc <- rbind(desc.p,desc.c)

#Just select the columns want for table (at this point n,m,sd,range)
desc1 <- desc[, c("n", "mean", "sd", "min", "max")]

row.names(desc1) <- c("Depression", "Anxiety", "Stress", "FES", "Hostile", "Warmth", 
              "Emotional problems" , "Hyperactivity", "Conduct", "Peer problems", "PTSD symptoms", "Fact-focused", "Emotion-focused", "Self-focused", "Negative", "Positive")

#Use the wrapper apa_table to make an apa table of the descriptive
apa_table(desc1,
          caption = "Means, standard deviations and range for the key measures",
          #note = "bottom part",
          align = c("l","c", "c", "c", "c"),
          col.names = c("Measure of interest", "N","Mean","SD","Minimum","Maximum" ),
          digits = c(0,0, 2,2,2,2),
          stub_indents = list("DASS" = c(1:3), "PARQ" = c(5,6), "SDQ" = c(7:10), "Communication" = c(12:14), "COVID Impact" = c(15,16))
          )

```

```{r, corrtablecomm, echo=FALSE, results='asis'}

#correlation table
corrmatrixcomm <-  dplyr::select(covid_data_child, ch_talk_about_1_num, ch_talk_about_2_num, ch_talk_about_3_num, ch_talk_about_4_num, ch_talk_about_5_num, ch_talk_about_6_num, ch_talk_about_7_num, ch_talk_about_8_num)

colnames(corrmatrixcomm) <- c("facts", "information", "child emotions", "parent emotions", "others' feelings", "reassurance", "didn't know what to say", "too upset")

xcomm <- corx(corrmatrixcomm,
          triangle = "lower",
          stars = c(0.05, 0.01, 0.001))

papaja::apa_table(xcomm$apa, # apa contains the data.frame needed for apa_table
                  caption = "Bivariate correlations for key variables and covariates (Pearson’s)",
                  note = "* p < 0.05; ** p < 0.01; *** p < 0.001. Not corrected for multiple comparisons. Full variable names: .",
                  landscape = TRUE,
                  #escape = F
                  )

#correlation plot
# Mcomm <- cor(corrmatrixcomm, use = "complete.obs")
# colnames(Mcomm) <- c("facts", "information", "child emotions", "parent emotions", "others' feelings", "reassurance", "didn't know what to say", "too upset")
# rownames(Mcomm) <- c("facts", "information", "child emotions", "parent emotions", "others' feelings", "reassurance", "didn't know what to say", "too upset")
# res1comm <- cor.mtest(corrmatrixcomm, use = "complete.obs",
#                    conf.level = .95)
#  
# corrplot.mixed(Mcomm,  order = "hclust", lower.col = "black", number.cex = .6,
#                 tl.col = "black", tl.srt = 45,tl.cex = 0.8, tl.pos= "lt",
#                 p.mat = res1comm$p, sig.level = .05, insig = "blank") 

```


# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
